---
title: "college_data"
author: "Anshuman Dikhit, dikhit2"
date: "12/21/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

function to de-factorize variables

```{r}
defactorize = function(var) {
  return(as.numeric(as.character(var)))
}
```



Import the entire dataset

```{r}
college_dataset = read.csv("../data/MERGED2015_16_PP.csv", header = TRUE)
head(college_dataset)
```

split and combine college name and location coordinates

```{r}
college_names = as.character(college_dataset$INSTNM) # Institution name
college_zipcodes = defactorize(college_dataset$ZIP) # Institution zip code
college_latitudes = defactorize(college_dataset$LATITUDE) # Institution latitude
college_longitudes = defactorize(college_dataset$LONGITUDE) # Institution longitude
college_data = data.frame(college_names, college_zipcodes, college_latitudes, college_longitudes)
head(college_data)
```

split and combine admission rates and % STEM degrees

```{r}
college_admission_rates = defactorize(college_dataset$ADM_RATE) # Insitution admission rate
college_STEM_degrees = defactorize(college_dataset$PCIP15) # Institution % of STEM Degrees given out
college_data = data.frame(college_data, college_admission_rates, college_STEM_degrees)
head(college_data)
```

split and combine University costs in state and out of state

```{r}
college_in_state_cost = defactorize(college_dataset$TUITIONFEE_IN) # Institution in state tuition
college_out_state_cost = defactorize(college_dataset$TUITIONFEE_OUT) # Institution out of state tuition
college_data = data.frame(college_data, college_in_state_cost, college_out_state_cost)
head(college_data)
```

split and combine family income quartile cost for public universities

```{r}
public_avg_cost_25 = defactorize(college_dataset$NPT41_PUB) # Average cost for $0-$30,000 family income
public_avg_cost_50 = defactorize(college_dataset$NPT42_PUB) # Average cost for $31,000-$48,000 family income
public_avg_cost_75 = defactorize(college_dataset$NPT43_PUB) # Average cost for $49,000-$75,000 family income
public_avg_cost_100 = defactorize(college_dataset$NPT44_PUB) # Average cost for $76,000-$110,000 family income
public_avg_cost_rest = defactorize(college_dataset$NPT45_PUB) # Average cost for +$110,000 family income
college_data = data.frame(college_data, public_avg_cost_25, public_avg_cost_50, public_avg_cost_75, public_avg_cost_100, public_avg_cost_rest)
head(college_data)
```

split and combine family income quartile cost for private universities

```{r}
private_avg_cost_25 = defactorize(college_dataset$NPT41_PRIV) # Average cost for $0-$30,000 family income
private_avg_cost_50 = defactorize(college_dataset$NPT42_PRIV) # Average cost for $31,000-$48,000 family income
private_avg_cost_75 = defactorize(college_dataset$NPT43_PRIV) # Average cost for $49,000-$75,000 family income
private_avg_cost_100 = defactorize(college_dataset$NPT44_PRIV) # Average cost for $76,000-$110,000 family income 
private_avg_cost_rest = defactorize(college_dataset$NPT45_PRIV) # Average cost for +$110,000 family income
college_data = data.frame(college_data, private_avg_cost_25, private_avg_cost_50, private_avg_cost_75, private_avg_cost_100, private_avg_cost_rest)
head(college_data)
```

split and combine Number of Title IV students

```{r}
title_4_public = defactorize(college_dataset$NUM4_PUB) # Number of students getting financial aid from Title IV
title_4_private = defactorize(college_dataset$NUM4_PRIV) # Number of students getting financial aid from Title IV
college_data = data.frame(college_data, title_4_public, title_4_private)
head(college_data)
```

split and combine faculty salary

```{r}
faculty_salary = defactorize(college_dataset$AVGFACSAL)
college_data = data.frame(college_data, faculty_salary)
head(college_data)
```

split and combine median debt upon graduation

```{r}
median_grad_debt = defactorize(college_dataset$GRAD_DEBT_MDN)
college_data = data.frame(college_data, median_grad_debt)
head(college_data)
```

Import dataset with all the information on salaries
split and combine variables on salary 2 years after graduation

```{r}
college_grad_salaries = read.csv("../data/Most-Recent-Cohorts-Treasury-Elements.csv", header = TRUE)
head(college_grad_salaries)
```

split and combine household income variable

```{r}
household_income = defactorize(college_grad_salaries$MEDIAN_HH_INC)
college_data = data.frame(college_data, household_income)
head(college_data)
```

split and combine percentile income 2 years after graduation

```{r}
grad_income_10th.2 = defactorize(college_grad_salaries$PCT10_EARN_WNE_P6)
grad_income_25th.2 = defactorize(college_grad_salaries$PCT25_EARN_WNE_P6)
grad_income_75th.2 = defactorize(college_grad_salaries$PCT75_EARN_WNE_P6)
grad_income_90th.2 = defactorize(college_grad_salaries$PCT90_EARN_WNE_P6)
college_data = data.frame(college_data, grad_income_10th.2, grad_income_25th.2, grad_income_75th.2, grad_income_90th.2)
head(college_data)
```

split and combine percentile income 6 years after graduation

```{r}
grad_income_10th.6 = defactorize(college_grad_salaries$PCT10_EARN_WNE_P10)
grad_income_25th.6 = defactorize(college_grad_salaries$PCT25_EARN_WNE_P10)
grad_income_75th.6 = defactorize(college_grad_salaries$PCT75_EARN_WNE_P10)
grad_income_90th.6 = defactorize(college_grad_salaries$PCT90_EARN_WNE_P10)
college_data = data.frame(college_data, grad_income_10th.6, grad_income_25th.6, grad_income_75th.6, grad_income_90th.6)
head(college_data)
```

create .csv file

```{r}
write.csv(college_data, "../data/college_data.csv", row.names = FALSE)
```




