---
title: "Exploring-College-Data"
author: "Curran Bhatia"
date: "11/12/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We will start by importing the data from The Wall Street Journal and Payscale regarding Salaries based on college.

```{r message=FALSE, warning=FALSE}
library(tidyverse)

```

```{r}

salaries = read_csv("Data/college-salaries/salaries-by-college-type.csv")
salaries

#as.numeric gsub ("[[punct]]")
x = salaries$`Mid-Career Median Salary`
#x = c("$135,359.00", "$135359.00", "$1,135,359.00")
y = sub('\\$','',x)
xy = as.numeric(sub('\\,','',as.character(y)))
salaries$`Mid-Career Median Salary` = xy
salaries

mid_career_df = tibble(salaries$`School Name`, salaries$`School Type`, salaries$`Mid-Career Median Salary`)

mid_career_df

colnames(mid_career_df) = c("name", "types", "median_salary")

types_colleges = unique(mid_career_df$types)

avg_midcareer = vector(mode="numeric", length= 5)
i = 1
for (x in types_colleges) {
  
  sal_filter = filter(mid_career_df, types == x)
  avg_midcareer[i] = mean(sal_filter$median_salary)
  
  i = i + 1
}
  
avg_midcareer

midcareer_type_df = tibble(types_colleges, avg_midcareer)
midcareer_type_df

ggplot(midcareer_type_df, aes(types_colleges, avg_midcareer)) + geom_col()

#Received help from: https://stat.ethz.ch/pipermail/r-help/2010-May/237909.html
# in order to change the characters into numbers
```

Now I want to plot the average salary based on type of school, Party, Engineering, Liberal Arts, State and Ivy. We don't necessarily need to tidy the data anymore than when we read it in, because it seems like all the columns have variables and rows have observations. Now I want to get the average salary per school type. 

